CP-SSA

### 2025-03-07 Code/R/Research/CP-SSA.Rmd
Cp-mssa research

### MSSA
```{r}
findL_mssa <- function() {
  noise <- rnorm(N, sd = sd)
  # noise <- gen_nswn(N, lambda = 10 / N)
  x <- matrix(s + noise, ncol = amp_period)

@@

### HO-MSSA
```{r}
findL_homssa <- function() {
  noise <- rnorm(N, sd = sd)
  # noise <- gen_nswn(N, lambda = 10 / N)
  x <- matrix(s + noise, ncol = amp_period)

@@

pulse_rmse_L_mssa <- function(R) {
  p <- progressor(R)
  future_replicate(R, {
    p()
    findL_mssa()
  }, simplify = "array", future.seed = 5) |> rowMeans() |> sqrt()
}

@@

pulse_rmse_L_homssa <- function(R) {
  p <- progressor(R)
  future_replicate(R, {
    p()
    findL_homssa()
  }, simplify = "array", future.seed = 5) |> rowMeans() |> sqrt()
}

>>>>

### MSSA for single-channel
```{r}
findL_mssa_single <- function() {
  noise <- rnorm(N, sd = sd)
  # noise <- gen_nswn(N, lambda = 10 / N)
  x <- matrix(s + noise, ncol = amp_period)

@@

### HO-MSSA for single-channel
```{r}
findL_homssa_single <- function() {
  noise <- rnorm(N, sd = sd)
  # noise <- gen_nswn(N, lambda = 10 / N)
  x <- matrix(s + noise, ncol = amp_period)

@@

pulse_rmse_L_mssa <- function(R) {
  p <- progressor(R)
  future_replicate(R, {
    p()
    findL_mssa_single()
  }, simplify = "array", future.seed = 5) |> rowMeans() |> sqrt()
}

@@

pulse_rmse_L_homssa <- function(R) {
  p <- progressor(R)
  future_replicate(R, {
    p()
    findL_homssa_single()
  }, simplify = "array", future.seed = 5) |> rowMeans() |> sqrt()
}
